Hydra Battles and Cie

### 2021-07-16 doc/part-hydras.tex
minor changes

    \index{hydras}{Projects}
    \begin{project}
      Prove that ordinal multiplication is left-distributive over ordinal addition; that is:
      $$\forall \alpha \, \beta \, \gamma < \epsilon_0, \alpha\times(\beta+\gamma) = \alpha\times\beta+ \alpha\times \gamma$$

    \end{project}
    \section{A variant for hydra battles}

>>>>

    \section{A refinement of \texttt{E0} : an ordinal notation for \texorpdfstring{$\omega^\omega$}{omega\^omega}}

    In Module   \href{https://github.com/coq-community/hydra-battles/blob/master/theories/ordinals/OrdinalNotations/OmegaOmega.v}{theories/ordinals/OrdinalNotations/OmegaOmega.v},
    we represent ordinals below $\omega^\omega$ by list of pairs of natural numbers (with the same coefficient shift as in \texttt{T1}).
    For instance, the ordinal $\omega^4\times 10 + \omega^3 + \omega+ 5$ is represented by the list \texttt{(4,9)::(3,0)::(1,0)::(0,4)::nil}.

  The usual operations : \texttt{succ}, \texttt{+}, \texttt{*} are simple variants of the same operations in \texttt{T1}.

    We establish this representation as a \emph{refinement} of the data types we used to represent ordinals less than $\epsilon_0$. Thus, many properties like well-foundedness of $<$ and associativity of $+$,  of this ordinal notations have very short proofs.

%ici
    \section{A variant for hydra battles}
